---
title: "theCLT"
author: "Syslee Evans"
date: '2022-06-23'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The resulting plot is unimodal because it peaks and then declines. The unimodal has 2 peaks and both peaks are the same size.

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

 The resulting plot is a unimodal because of the different peaks, there are 3 different peraks the 2 smallest are the same size and the one in the middle is the biggest size.

Do this again for 4 random samples
```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")
print(mean(x.avg))
print(sd(x.avg))
```

Then again for 9 random samples
```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")
print(mean(x.avg))
print(sd(x.avg))
```

then 16 random samples
```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")
print(mean(x.avg))
print(sd(x.avg))
```
finally for 36 random samples.
```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")
print(mean(x.avg))
print(sd(x.avg))
```
Write a summary paragraph describing what you observed and how it relates to the central limit theorem.


Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.